Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-02-28 introduction.tex
working on introduction

Over the last three decades there have been multiple efforts to better estimate the seismic hazard and assess seismic risk in Iran \citep[e.g.,][]{Tavakoli1999} [\textcolor{red}{Add at least two more references here}]. These studies have been, in part, intended to help improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}. While such improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest that seismic risk is high and therefore more complete and accurate assessments of seismic hazard are necessary.

We are particularly interested in the assessment of seismic hazard in northern Iran. This region has a significant population density with respect to the rest of the country, and includes some of its most populated cities: Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, and Rasht. These cities alone house about 31.5 million people. They represent nearly 40 percent of the total population of Iran and a good portion of its economic activity. In this study we ...

In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\

>>>>

Over the last three decades there have been multiple efforts to better estimate the seismic hazard and assess seismic risk in Iran \citep[e.g.,][]{Tavakoli1999} [\textcolor{red}{Add at least two more references here}]. These studies have been, in part, intended to help improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}. While improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest high levels of seismic and therefore more complete and accurate assessments of seismic hazard, that incorporate the latest available data and alternative methods, are necessary.

In this article, we are particularly interested in the assessment of the seismic hazard of northern Iran. This region houses nearly 40 percent (31.5 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, and Rasht; and has suffered the devastating effects of earthquakes in the past (e.g., \textcolor{red}{two references}). Due to its importance, northern Iran has recently been the subject of various efforts to better characterize seismic hazard in the region \citep[e.g.,][]{Ghodrati2011, Abdollahzadeh2014a, Boostan2015} \textcolor{red}{[Are these good references? we need them to be about northern Iran. Any other?]}. In general, these studies highlight the significant seismic hazard of the region, and... \textcolor{red}{[need punch line conclusions here]}. However useful, most previous studies focus on particular locations (e.g., Tehran) or are based on the categorization of seismogenic faults, which are often subjectively interpreted and limited to the availability data. Here, we use the smoothed seismicity method introduced by \citep{Frankel1995}. This approach to map seismic hazard has been used with success in other regions (\textcolor{red}{[two references needed here]}). Its major feature is the treatment of recorded and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting. While we recognize that probabilistic seismic hazard analysis based on fault systems can be more realistic and accurate, by choosing the smoothed seismicity method we seek to reduce the uncertainty associated with fault mapping and

The method is solely based on cataloged

features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis. This method is simpler for hazards calculation and is based solely on recorded seismicity history. In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.

% To assess the seismic hazard for this region, we use the smoothed seismicity method introduced by \citep{Frankel1995}. In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh; but for completeness, we also consider the partial contribution of the areas of Zagros and the central-east seismic zones within our domain of interest (see Figure \ref{fig:Iran}).

An important aspect of seismic hazard is the proper definition of attenuation parameters. In a recent effort, \citet{Zafarani2014} reviewed multiple available ground motion prediction equations available in the literature and concluded that the most appropriate attenuation relationship to be used in northern Iran, int he Alborz and Kopeh-Dagh regions, was

% \citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran. The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.

\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran. The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region. Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.

which may cause significant damage to northern Iran. Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions. In this study we use an updated catalog and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity. We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran. This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.

has a significant population density

with respect to the rest of the country, and includes some of its most populated cities: . Not accounting for rural areas,

these cities house about 31.5 million people, which represents nearly 40 percent of the total population of Iran.

Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh. For completeness, we also consider the partial contribution of the two remaining seismic zones to the south, that is, Zagros to the southwest, and the south-central and southeastern Iranian seismic zones.

we used smoothed seismicity approach \citep{Frankel1995} in order to do seismic hazard analysis. We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopeh Dagh. We also consider seismicity of part of Central-East Iran and Zagros regions. We computed seismic parameters and catalog completeness in these regions. Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.  We consider the $Mw \  5$ earthquake as a threshold magnitude  for structural damage. In order to consider damage to the historical masonry building (which includes most part of big cities and rural areas) we also considered $Mw \  4.5$ as a threshold for structural damage to these kind of building.

% in which many destructive earthquakes have been reported.

% continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures. In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
